\section{Biomes}\label{ch:World:Biomes}

Let us begin by talking about the different biomes within the world. These are
more or less hospitable in general and for some tribes specifically. They are
defined by different flora, fauna and resource abundance. A short summary is
provided here.

\begin{longtable}{lllll}
	\toprule
	Biome           & Trees   & Fertility & Animal-Danger & Minerals \\
	\midrule
	\Gls{Grassland} & Low     & Medium    & Lowest        & Lower    \\
	\Gls{Forest}    & Higher  & Medium    & Low           & Lower    \\
	\Gls{Jungle}    & Highest & Highest   & Higher        & Lowest   \\
	\Gls{Desert}    & Lowest  & Lower     & Higher        & Medium   \\
	\Gls{Mountain}  & Lower   & Lowest    & Higher        & Highest  \\
	\bottomrule
\end{longtable}

\subsection{\Glsfmttext{Grassland}}\label{ch:World:Biomes:Grassland}

The \Gls*{Grassland} is the kindest of all biomes. It is fertile for farming,
hosts rather tame wildlife and few trees. Between the rocks some resource veins
might be discovered.

\subsection{\Glsfmttext{Forest}}\label{ch:World:Biomes:Forest}

The \gls*{Forest} is quite similar to the \gls{Grassland}, but hosts some more
hostile wildlife and an abundance of trees. Within it mushrooms and herbs
flourish and a few resource veins can be found.

\subsection{\Glsfmttext{Jungle}}\label{ch:World:Biomes:Jungle}

The \gls*{Jungle} is lush and fertile. Rare in minerals rich in dangerous
animals it is not well suited for most tribes. If the animals can be tamed and
the trees uprooted it is the most fertile biome.

\subsection{\Glsfmttext{Desert}}\label{ch:World:Biomes:Desert}

The endless dry sand and rock of the \gls*{Desert} hosts almost no life. The
animals that roam there are dangerous. The only fertile spots are found along
rivers and oasis. While it is poor land for farming it is excellent for mining,
giving a boost to the tribes that can tame this terrain.

\subsection{\Glsfmttext{Mountain}}\label{ch:World:Biomes:Mountain}

Bare rock bears no fruit and so no tribe can live on the \gls*{Mountain} alone.
Despite that and the more dangerous wildlife the rich ore veins and the
abundance of rock encourage the tribes to build mining outposts within to feed
their growing industry.

\subsection{\Glsfmttext{Sea}}\label{ch:World:Biomes:Sea}

The \gls*{Sea} is not a biome that can be inhabited by the tribes, but its
bounty they can use.
