\section{Inhabitants}\label{ch:World:Inhabitants}

The world is inhabited by sapient creatures mostly organized into the various
\hyperref[ch:Tribes]{tribes} and animals. The animals fall into two general
categories \hyperref[ch:World:Inhabitants:Animals]{wild animals} and
\hyperref[ch:World:Inhbitants:Livestock]{livestock}.

All of them share a few general characteristics, like the \emph{speed} they
move or the \hyperref[ch:Conflict:Combat]{harm} they can absorb before
suffering severe consequences. These vary from species to species. Please note
that \hyperref[ch:World:Inhabitants:Sapients]{sapients} may significantly
modify these values, by \gls{Equipment}, \gls{Drink}, \gls{Medicine},
\gls{Weapon} and \gls{Armor}.

\begin{longtable}{l l lll lll}
	\toprule
	Species    & Speed  & \multicolumn{3}{c}{Resistance} & \multicolumn{3}{c}{Regeneration}                                        \\
	           &        & Physical                       & Stun                             & Morale & Physical & Stun   & Morale  \\
	\midrule
	\Gls{Boar} & Medium & Low                            & Medium                           & Medium & High     & Higher & Highest \\
	\Gls{Deer} & Higher & Lowest                         & Low                              & Lowest & High     & Higher & Hight   \\
	Human      & Medium & Medium                         & Medium                           & Medium & Medium   & Medium & Medium  \\
	\bottomrule
\end{longtable}

\subsection{Wild animals}\label{ch:World:Inhabitants:Animals}

Wild animals roam the different biomes. Some \hyperref[ch:Tribes]{tribes} hunt
them for a variety of \hyperref[ch:Goods:Nature:Animals]{goods}, but their
numbers are small and they replenish slowly, which makes them a finite
resource. Only the \gls{Vikings} can use them for a sustainable economy,
because their \hyperref[ch:Tribes:Vikings:Religion:Forest]{sanctuaries}
replenish them.

In addition to the general attributes of all inhabitants, they are also
described by the \emph{Danger} they pose to other inhabitants, the
\emph{aggression} they exhibit towards them. and their occurrence in different
\hyperref[ch:World:Biomes]{biomes}.

\begin{longtable}{llllllll}
	\toprule
	Animal     & Danger & Aggression & \Gls{Grassland} & \Gls{Forest} & \Gls{Jungle} & \Gls{Desert} & \Gls{Mountain} \\
	\midrule
	\Gls{Boar} & Low    & Low        & Lower           & Medium       & Lower        & None         & None           \\
	\Gls{Deer} & Lowest & None       & Lowest          & High         & None         & None         & None           \\
	\bottomrule
\end{longtable}

\paragraph{\Glsfmttext{Boar}}
\Glspl*{Boar} dwell on the grassland and the forest. They are hunted for their
\gls{Meat} and \glspl{Hide} and often fight back against the hunters.

\paragraph{\Glsfmttext{Deer}}
\Gls{Deer} are forest dwellers. They pose no danger to the tribes and flee, when
spotted or attacked. They are hunted for \gls{Meat} and \glspl{Hide}.

\subsection{Livestock}\label{ch:World:Inhabitants:Livestock}

The \hyperref[ch:Tribes]{tribes} keep different animals as livestock to produce
a variety of different \hyperref[label]{goods}. Some of these animals need to
graze and some need to be fed. This list gives a rough summary of all of them.

\subsection{Sapients}\label{ch:World:Inhabitants:Sapients}

Sapients are all sapient creatures. The biggest group are the members of the
\hyperref[ch:Tribes]{tribes}, but it refers to all inhabitants that can use
weapons or equipment.

Those all have two kind of needs, \emph{necessary} needs like \gls{Sustenance}
or \gls{Sleep}, that lead to sever consequences if not fulfilled and
\emph{additional} needs like \gls{Clothing}, which influence their Happiness.
The \emph{necessary} vary among species and the \emph{additional} needs vary
among culture.

Opposed to necessary needs \emph{additional} needs often come with an expected
quality. So while sapients will eat everything for \gls{Sustenance}, they are
more picky for \gls{Dining}. If the \gls{Food} offered is not of sufficient
quality, they will satisfy their need for \gls{Sustenance}, but their need for
\gls{Dining} will stay untouched, leading either to a decrease in happiness or
the consumption of another higher quality \gls{Food}.

While all \emph{additional} needs only influence Happiness by using
\gls{Merchandise} \emph{necessary} needs have different effects:

\begin{longtable}{ll}
	\toprule
	Need             & Effect if unfulfilled \\
	\midrule
	\Gls{Sustenance} & Death                 \\
	\Gls{Sleep}      & Unconsciousness       \\
	\bottomrule
\end{longtable}

As sapients by our definition use \gls{Equipment}, \glspl{Tool}, \gls{Armor}
and \glspl{Weapon} they need to hold them. So sapients have different slots for
these things. Feet for \glspl{Shoe}, hands for \glspl{Weapon} and \glspl{Tool}
and heads and bodies for \gls{Armor}.

\subsubsection{Humans}\label{ch:World:Inhabitants:Sapients:Humans}

Humans are the dominant species in the world their \hyperref[ch:tribes]{tribes}
erect great and powerful cities and wage \hyperref[ch:Conflict]{war} against
each others. Here they are categorized as described above.

\begin{longtable}{ll}
	\toprule
	Need             & Strength \\
	\midrule
	\Gls{Sustenance} & Medium   \\
	\Gls{Sleep}      & Medium   \\
	\bottomrule
\end{longtable}

\begin{longtable}{lll}
	\toprule
	Slot         & Amount & Items                                    \\
	\midrule
	Pair of feet & 1      & \Glspl{Shoe}                             \\
	Head         & 1      & \Gls{Helmet}                             \\
	Body         & 1      & \Gls{BodyArmor}                          \\
	Hands        & 2      & \Gls{Tool}, \gls{Weapon}, \glspl{Shield} \\
	\bottomrule
\end{longtable}
