\section{Plants}\label{ch:World:Plants}

The world is home to a wide variety of different plants. Some of these are
abundant, covering the soil in the different \hyperref[ch:World:Biomes]{biomes}
like \gls{Grass} in the \gls{Grassland}. Others are more rare like
\glspl{AppleTree} or \glspl{Mushroom}. These section deals with all of them.

\subsection{Abundant plants}\label{ch:World:Plants:Abundant}

Abundant plants grow so fast and plentiful that they are not tracked
individually, instead the surface layer on most
\hyperref[ch:World:Biomes]{biomes} is covered in them. So we list them
according to the \hyperref[ch:World:Biomes]{biomes} they appear in.

\begin{longtable}{llllll}
	\toprule
	Plant       & \multicolumn{5}{c}{\hyperref[ch:World:Biomes]{Biome} occurrence}                                                               \\
	            & \Gls{Grassland}                                                  & \Gls{Forest} & \Gls{Jungle} & \Gls{Desert} & \Gls{Mountain} \\
	\midrule
	\Gls{Grass} & Highest                                                          & Medium       & None         & None         & Lower          \\
	\Gls{Moss}  & Lowest                                                           & Higher       & Lower        & None         & Medium         \\
	\bottomrule
\end{longtable}

\subsubsection{\Glsfmttext{Grass}}

\Gls*{Grass} covers the ground within the \gls{Forest} and the \gls{Grassland}.
Some \hyperref[ch:World:Inhabitants:Livestock]{livestock}.
needs to graze to live. This can only happen on soil covered with \gls{Grass} or similar abundant plants.

\subsubsection{\Glsfmttext{Moss}}

\Gls*{Moss} is a abundant plant that can be consumed by some \hyperref[ch:World:Inhabitants:Livestock]{livestock}.
\Gls*{Moss} covers the ground within the \gls{Forest} and can be used to graze some \hyperref[ch:World:Inhabitants:Livestock]{livestock}.

\subsection{Rare Plants}\label{ch:World:Plants:Rare}

Most plants may be plentiful, but they are not abundant, so in contrast to the
\hyperref[ch:World:Plants:Abundant]{abundant plants} they are called rare
plants. They grow slower than \hyperref[ch:World:Plants:Abundant]{abundant
	plants}, making it necessary to describe their \emph{growth} separately. They
also produce a variety of \hyperref[ch:Goods:Nature:Plants]{goods} utilized in
the economies of the \hyperref[ch:Tribes]{tribes}.

\begin{longtable}{lllllll}
	\toprule
	Plant                & Growth & \multicolumn{5}{c}{\hyperref[ch:World:Biomes]{Biome} occurrence}                                                               \\
	                     &        & \Gls{Grassland}                                                  & \Gls{Forest} & \Gls{Jungle} & \Gls{Desert} & \Gls{Mountain} \\
	\midrule
	\Gls{Plant:Herb}     & High   & Lower                                                            & Low          & Low          & None         & Lowest         \\
	\Gls{Plant:Mushroom} & Medium & Lowest                                                           & Low          & Low          & None         & Lowest         \\
	\Gls{Fir}            & Low    & None                                                             & High         & None         & None         & Low            \\
	\Gls{Oak}            & Lowest & Lower                                                            & Low          & None         & None         & Lowest         \\
	\Gls{AppleTree}      & Lower  & Lower                                                            & Low          & Low          & None         & None           \\
	\Gls{ChestnutTree}   & Lower  & Lower                                                            & Low          & None         & None         & None           \\
	\bottomrule
\end{longtable}

\subsubsection{\Glsfmttext{Plant:Herb}}

Within the forest medicinal \glspl*{Plant:Herb} grow. They are
\glslink{Herb}{harvested} and often used to prepare \gls{Food}, \gls{Medicine}
or \gls{Drink}.

\subsubsection{\Glsfmttext{Plant:Mushroom}}

\Glspl*{Plant:Mushroom} grow mostly within the \gls{Forest} and the \gls{Jungle}.
They are \glslink{Mushroom}{collected} and used
to prepare \gls{Food}, \gls{Medicine} or \gls{Drink}.

\subsubsection{\Glsfmttext{Fir}}

\Glspl*{Fir} grow within the \gls{Forest} and can be felled for \gls{Timber}.

\subsubsection{\Glsfmttext{Oak}}

\Glspl*{Oak} dot the \gls{Forest} and \gls{Grassland} and can be felled for \gls{Timber}.

\subsubsection{\Glsfmttext{AppleTree}}

Within the \gls{Grassland} and the \gls{Forest} the \glslink{Apple} {fruit} of
apple trees can be collected, unless they are cut down for \gls{Timber}.

\subsubsection{\Glsfmttext{ChestnutTree}}

The \Glsfmttext{ChestnutTree} grows in the \gls{Grassland} and the \gls{Forest}
and their \glslink{Chestnut}{nuts} can be consumed by
\hyperref[ch:World:Inhabitants]{creatures} creatures passing by or cut down for
\gls{Timber}.