\newglossary*{tribe}{Tribes}
\newglossaryentry{Vikings}{
	name=children of the spirits,
	type=tribe,
	description={simple nature loving craftsmen,
		with a strong connection to the land and nature that surrounds them}
}
\newglossaryentry{Nomads}{
	name=mounted men,
	type=tribe,
	description={fierce warriors and raiders, that raise large herds and conquer their foes
		on the back of their mounts with their cruel gods and the wind in their back}
}
\newglossaryentry{Egyptians}{
	name=river folk,
	type=tribe,
	description={erect great monuments within fertile river plains.
	They fight for the glory of their kings and an immortal afterlife.}
}
\newglossaryentry{Aztecs}{
	name=servants of the serpent,
	type=tribe,
	description={need to feed the sky serpent with human sacrifice so it can then be
		consumed by sun.
		Born from corn and water they are constantly on the search for new sacrifices.
		For the serpent hungers and if you do not feed it, it will consume you}
}
\newglossaryentry{Japanese}{
	name=empire,
	type=tribe,
	description={lies within the fertile plains-
		Its peasants grow rice, its craftsman forge tools and weapons,
		so its priest and artists can create great works for the celestial dragons.
		Its warriors defend the borders with bow, katana and musket against all invaders}
}
\newglossaryentry{Romans}{
	name=republics,
	type=tribe,
	description={stand against the gods.
	Where other chose slavery in the face of the supernatural the republics chose industry and science.
	Heavily armored its legions advance towards its enemy,
	while the mortars turn fertile plains into burning hell.
	The complex bureaucracy and trade deals enable the republics to field
	powerful legions commanded by officers and supported by fearsome war-machines,
	to lay low all that oppose the might of humanity}
}
