\section{Natures bounty}\label{ch:Goods:Nature}

The world is rich in countless natural resources the
\hyperref[ch:Tribes]{tribes} can use. They can be categorized in according to
their source. Some come from \hyperref[ch:World:Inhabitants:Animals]{animals},
some from the \hyperref[ch:World:Minerals]{ground} and some from
\hyperref[ch:World:Plants]{plants}. They and their sources are discussed here.

\subsection{Plants}\label{ch:Goods:Nature:Plants}

The world is home to a wide variety of plants. Plants can be categorized into
plants of special interesting like trees or herbs and abundant plants. Abundant
usually cover large areas and are to abundant to track. \emph{Grass} is a good
example. In the following list all special plants will be listed with the
\emph{fruit} they create continuously and the resources they can be
\emph{harvested} for.

\begin{longtable}{llllll}
	\toprule
	Plant         & Fruit    & Harvest        & Biome             & Growth & Abundance \\
	\midrule
	Herb          & None     & \Gls{Herb}     & Forest            & High   & Low       \\
	Mushroom      & None     & \Gls{Mushroom} & Forest            & Medium & Low       \\
	Fir           & None     & \Gls{Timber}   & Forest            & Low    & High      \\
	Oak           & None     & \Gls{Timber}   & Forest, Grassland & Lowest & Lower     \\
	Apple-tree    & Apple    & \Gls{Timber}   & Forest, Grassland & Lower  & Lower     \\
	Chestnut-tree & Chestnut & \Gls{Timber}   & Forest, Grassland & Lower  & Lower     \\
	\bottomrule
\end{longtable}

\subsection{What grows in abundance}\label{ch:Goods:Nature:Plants:Abundant}

Abundant plants usually cover the entire ground of a Biome, therefore they are
not tracked separately.

\paragraph{Grass}

Grass covers the ground within the forests and the grasslands. Some livestock
needs to graze to live. This can only happen on grassland. The grass grows fast
enough so it is not affected by the grazing.

\subsection{What grows and is searched}\label{ch:Goods:Nature:Plants:Limited}

Most plants are limited in their occurrence. So while they regrows their total
number within an area is limited. The easiest way to understand the concept are
trees. A grove consists of a few trees, once they are felled they are gone.
Mushrooms, herbs and other plants follow a similar principle.

\paragraph{Herbs}

Within the forest medicinal herbs grow. These are can also be used as a food
additives.

\paragraph{Mushromm}

Mushrooms grow within the forest and can be used for medical purposes or as
food.

\paragraph{Fir}

The fir grows within the forest and can be felled for timber.

\paragraph{Oak}

Oak trees dot the forest and grassland and can be felled for timber.

\paragraph{Apple-tree}

Within the grassland and the forest the fruit of apple trees appear, unless
they are cut down for timber.

\paragraph{Chestnut-tree}

The Chestnuts grow in the grassland and the forest and are often consumed by
wild animals, but some of the tribe appreciate them too, others just see
valuable building material in them.

\subsection{Animals}\label{ch:Goods:Nature:Animals}

Within the world there are countless
\hyperref[ch:World:Inhabitants:Animals]{wild animals}. These can be hunted and
butchered for different goods. They are also joined by the
\hyperref[ch:World:Inhabitants:Livestock]{livestock} that the
\hyperref[ch:Tribes]{tribes} keep. The goods and from which animal they can be
sourced are found here.

\begin{longtable}{ll}
	\toprule
	Good       & Sources                \\
	\midrule
	\Gls{Hide} & \Gls{Boar}, \gls{Deer} \\
	\Gls{Meat} & \Gls{Boar}, \gls{Deer} \\
	\bottomrule
\end{longtable}

\subsection{The sea}\label{ch:Goods:Nature:Sea}

The seas teem with life. The fish within them are caught by the fishers for
sustenance.

\subsection{Minerals}\label{ch:Goods:Nature:Minerals}

Within the worlds above the ground valuable resources often appear agglomerated
within nodes. From these nodes these \hyperref[ch:World:Minerals]{minerals} can
be mined.

\paragraph{\Glsfmttext{Stone}}

\Gls*{Stone} can be directly mined and then used as a
\hyperref[ch:Goods:Materials]{building material}
or for the production of other goods.

\paragraph{\Glsfmttext{CopperOre}}

\Gls*{CopperOre} is used to make the softest metal used for \glspl{Weapon}, \glspl{Tool} and \glspl{Armor}, \gls{Copper}.

\paragraph{\Glsfmttext{IronOre}}

\Gls*{IronOre} is the prerequisite for \gls{Iron} a medium metal for \glspl{Weapon}, \glspl{Tool} and \glspl{Armor}.
\Gls{Iron} can also be refined into \Gls{Steel}.

\paragraph{\Glsfmttext{SilverOre}}

\Gls*{Silver} is a rare metal use to produce \gls{Merchandise}.

\paragraph{\Glsfmttext{GoldOre}}

\Gls*{Gold} is a rare metal use to produce high value \gls{Merchandise}.

\paragraph{\Glsfmttext{Coal}}

\Gls*{Coal} be mined and used as a fuel. \Gls*{Coal} is often used to refine other metals from ores.
